// updated on 12 april 2023 

\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}
%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons 
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper]{altacv}

% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

% Change the font if you want to.

% If using pdflatex:
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}

% this is excess package from chatGPT to change the colors 
\usepackage{xcolor}
% \usepackage{hyperref}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Navy}{HTML}{000080}
\definecolor{SlateGrey}{HTML}{404241}
\definecolor{LightGrey}{HTML}{211d1c}
\colorlet{heading}{Navy}
\colorlet{accent}{Navy}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
%% sample.bib contains your publications
\addbibresource{sample.bib}

\usepackage[colorlinks]{hyperref}

\begin{document}
\name{Shantanu Pawar.}
\break
\tagline{}

\personalinfo{%
\divider
\fontsize{10}{14}\selectfont

 \mailaddress{\href{mailto:shantanupawar292@gmail.com}{\textcolor{black}{\bf shantanupawar292@gmail.com}}}
  \phone{(+91) 73859 52851}
\linkedin{\href{https://www.linkedin.com/in/shantanu-pawar/} {\textcolor{black}{\bf Linkedin}} }
\github {\href{https://github.com/Shantanu-pawar} {\textcolor{black}{\bf Github}} }

\smallskip \smallskip \smallskip \smallskip
\item {A dedicated entry-level software developer proficient in Spring Boot, JSP, and algorithms, with a strong problem-solving and a commitment to delivering high-quality code.
}

% \birthday{Date Of Birth : 21-08-2000}
}


%% Make the header extend all the way to the right, if you want. 
\begin{fullwidth}
\makecvheader

\end{fullwidth}

\divider


\cvsection[page1sidebar]{PROJECTS}
\smallskip

% Major chat application project 

% \cvevent{\textbf{GupShup - Real Time Chat WebApp}} {}{}{}
% \smallskip  
% \begin{itemize}
% \item Provide a platform to chat realtime with \textbf{friends}
% \smallskip 
% \item Users can send \textbf{text messages, photos}, etc
% \smallskip 
% \item We can also create \textbf{group} of multiple users and chat ingroup.
% \smallskip 
% \item User's can also \textbf{delete or update} profile.
% \smallskip 
% \item \textbf{Languages and Technology} : React-Js, JavaScript, Firebase.
% \end{itemize}
% \medskip


\cvevent {\href{https://github.com/Shantanu-pawar/High-level-parking-lot-Design}{\textcolor{black}{\faGithub} \textcolor{black}{\bf Parking lot System design.}}} {}{}{}

\begin{itemize}

% sequence to write project description : 
% 1 point - technology used ?
% 2. what is key features of your project ? - make sure to highlight the features
% 3 .wahtever one extra upgrede or you wanna write down just write it
\item primary goal of the system is to automate the parking process
\item The system tracks parking spots availability and \textbf{displays it to users in real-time, so it saves the time.}

\item  Users can pay for parking and \textbf{ system automatically generates a bill} based on the parking duration.
    
\end{itemize}
\medskip
\divider


% project - merge sort

\cvevent {\href{https://github.com/Shantanu-pawar/Merge-sort-visualiser}{\textcolor{black}{\faGithub} \textcolor{black}{\bf Merge Sort visualiser}}} {}{}{}

\begin{itemize}


\item \textbf{Languages and Technology} : React-Js, JavaScript. 
\item Main aim of this project is to understand how it can sort \textbf{large Datasets efficiently.}
\item The system \textbf{allows users to control the animation speed}, enabling them to slow down or \textbf{speed up the sorting process} as needed.

\item  The system can \textbf{generate random datasets} of various sizes to test the Merge Sort algorithm's efficiency.

\end{itemize}
\medskip

\divider


\cvsection{Intern experience}
\cvevent{\textbf{TRAINING - Full Stack Web Development}}{Acciojob}{Sept 2022 -- present}{Delhi}
\divider
\medskip

\cvevent{\textbf{INDO-GERMAN TOOL ROOM}}{at Indore Government Tool Room, Indore, India} 
{NOV 2019 -- 1 Month }{Indore.}
\begin{itemize}
    \smallskip  \smallskip

\item Gained practical knowledge of CNC and milling machines Using their programming languages G-code and M-code
    \smallskip  \smallskip

\item Acquired knowledge of quality control 
    \smallskip  \smallskip

\item inspect several techniques to ensure precision and accuracy in manufactured parts.

\end{itemize}
\medskip

\cvsection{Achievements}
\smallskip
\begin{itemize}
\item I have solved 300+ questions on different coding platforms like Leetcode, GFG, HackerRank.
\smallskip  \smallskip

\item I got the National Cadet Corps A 'set certificate ,Scholorship.
    \smallskip  \smallskip

\item Elected Member of MESA committee
    \smallskip  \smallskip

\item Won 1st price in Impulse Technical Festival event - Design of AeroDynamics to eliminate Resistance - Using AutoCad.
    \smallskip  \smallskip

\end{itemize}

\clearpage
\end{document}


// --------------------------------------------------------------------------------------------------------------------------

\cvsection{Education}
\cvevent{\textbf{B.Tech}} {Mechanical Engineering}{ JUL 2019 - SEPT 2022 \hspace{0.8 cm} CGPA : 8.6 }{}
\smallskip  \smallskip

\cvevent{\textbf{Deploma - Mechanical}}{Ssvps BSD Polytechnic, Dhule.}{ AUG 2016 - MAR 2019 \hspace{2.25 cm} }{}
\smallskip  \smallskip

\cvevent{Class 10th }{JaiHind high School - SSC}{ June 2016   \hspace{1.8 cm}    PA : 78.60 \% }{}
\smallskip  \smallskip

% \divider


\cvsection{Skills}

\cvtag{Java}
\cvtag{HTML}
\cvtag{CSS}
\cvtag{Data Structure's}
% \cvtag{SQL}
\cvtag{Tools : Git, VS code}

%% Yeah I didn't spend too much time making all the 
%% spacing consistent... sorry. Use \smallskip, \medskip, 
%% \bigskip, \vpsace etc to make ajustments.
\medskip

\cvsection{certificates}
\smallskip 

\begin{itemize}
\smallskip
\item INDO-GERMAN TOOL ROOM program.
\smallskip
\smallskip
\item National Cadet Corps Camp Training Certificates.
\smallskip
\smallskip
\item 48 Maharashtra BN NCC ,Delhi, India.
\smallskip
\smallskip
\end{itemize}



\cvsection{COURSEWORK}
\begin{itemize}
    \item Introduction to Programming.
        \smallskip  \smallskip

    \item Data Structure's.
        \smallskip  \smallskip

    \item Analysis of Algorithms.
        \smallskip  \smallskip

    % \item Database Management Systems.
    %     \smallskip  \smallskip

\end{itemize}


\cvsection{EXTRA CURRICULAR}
\smallskip
\begin{itemize}
    \item I have done the National Cadet Corps 2yrs training successfully.
    \smallskip  \smallskip
    \item Teamwork and Collaboration 
        \smallskip  \smallskip
    \item Critical thinking and alway's try new problems for solve.
        \smallskip  \smallskip
    \item Command on interpersonal and communication skills.
        \smallskip  \smallskip

\end{itemize}


% \cvsection{LANGUAGEs} 
% \smallskip
% \smallskip
% \cvtag{English}
% \cvtag{Hindi}
% \cvtag{Marathi}

\medskip
